---
title: "Alcohol vs Seat choice"
author: "Trevor Ragazzo"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

According to the boxplot it shows that the back row seems to consume more alcohol than both the front and middle row. The front and middle rows are very slim and around the same amount of consumption. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The people sitting in the back have an overall higher score of alcohol consumption. They are about three times more than the middle rows and way more than the front row. The front row has a very small percentage of alcohol compared to the back. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The results from this graph shows a very small number so we will change up the graph to see if any information will change, or give us a better understanding of the data. 

```{r}
plot(TukeyHSD(model1))
```

Looking at the graph we see that the middle-back and the middle-front intervals are less than zero we should see significant results. 

## Conclusions

The results we saw in the different graphs were the people sitting in the back rows seem to have more alcohol consumption. But the back row had 32 people sitting there and comparing to the middle row having 82 people, of course the back would be a higher percentage because of the large amount of people in the middle 

